Appendix

### 2020-05-28 manuscript/bef_stability/appendix.Rmd
Fix result PCA with two axis

```{r eig-plot}
rotated_eigen_values <- 
  tibble(
    name = paste0("RC", seq(1,14)),
    type = c(rep("Kept", 5), rep("No kept", 9)),
    value = pca_rotated$rotated$values
  )
eigen_rotated_plot <-
  ggplot(rotated_eigen_values,
    aes(x = reorder(name, -value) , y = value)) +
  geom_col(aes(fill = type)) +
  scale_fill_discrete(name = "Status") +
  labs(x = "Rotated component", y = "Eigen values")
```

@@

loadings_pca <- matrix(
  as.matrix(round(pca_rotated$rotated$Structure, 2)),
  nrow = 14,
  dimnames = dimnames(pca_rotated$rotated$Structure)
  ) %>%
  as_tibble %>%
  mutate(
    Variable = str_replace_all(
      dimnames(pca_rotated$rotated$Structure)[[1]],
      pca_var_replacement)
  ) %>%
  select(Variable, RC1, RC2, RC3, RC4, RC5)

kable(
  x = loadings_pca,
  format = "latex",
  booktabs = T,
  label = "contrib-pca",
  caption = caption_contrib_pca
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r pca-rotated, fig.cap = pca_caption, fig.asp = 1}
p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)

pca_plot <- plot_grid(p1, p2, p3, eigen_rotated_plot, nrow = 2)
save_plot(
  filename = mypath("manuscript", "bef_stability", "figs", "pca_plot.pdf"),
  pca_plot,
  nrow = 2, ncol = 2,
  base_height = 6/2.54, base_asp = 1, base_width = NULL 
  )
pca_plot
```

@@

>>>>

```{r eig-plot}
rotated_eigen_values <- 
  tibble(
    name = paste0("RC", seq(1,14)),
    type = c(rep("Kept", 2), rep("No kept", 14 - 2)),
    value = pca_rotated$rotated$values
  )
eigen_rotated_plot <-
  ggplot(rotated_eigen_values,
    aes(x = reorder(name, -value) , y = value)) +
  geom_col(aes(fill = type)) +
  scale_fill_discrete(name = "Status") +
  labs(x = "Rotated component", y = "Eigen values")
```

@@

loadings_pca <- matrix(
  as.matrix(round(pca_rotated$rotated$Structure, 2)),
  nrow = 14,
  dimnames = dimnames(pca_rotated$rotated$Structure)
  ) %>%
  as_tibble %>%
  mutate(
    Variable = str_replace_all(
      dimnames(pca_rotated$rotated$Structure)[[1]],
      get_pca_var_name_replacement())
  ) %>%
  select(Variable, RC1, RC2)
kable(
  x = loadings_pca,
  format = "latex",
  booktabs = T,
  label = "contrib-pca",
  caption = caption_contrib_pca
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r pca-rotated, fig.cap = pca_caption, fig.asp = 1}
p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
#p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
#p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)

pca_plot <- plot_grid(p1, eigen_rotated_plot, nrow = 1)
save_plot(
  filename = mypath("manuscript", "bef_stability", "figs", "pca_plot.pdf"),
  pca_plot,
  nrow = 1, ncol = 2,
  base_height = 6/2.54, base_asp = 1, base_width = NULL 
  )
pca_plot
```

@@

```{r stab-network, eval = FALSE}
sem_data %>%
  select(sync, cv_sp, ct, t_lvl) %>%
  gather(network, metrics, ct, t_lvl) %>%
  gather(stab_comp, value, sync, cv_sp) %>%
  ggplot(aes(y = value, x = metrics)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(stab_comp ~ network, scales = "free_x")

stab_ct_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab_std ~ ct + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
stab_ct_ci <- confint(stab_ct_boot)

stab_ct_sum <- piecewiseSEM::rsquared(stab_ct_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_ct_pred <- pred_stab_ct_mod %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

# get coeff
coef_stab_ct <- map(list(stab = stab_ct_mod), fixed.effects)

stab_tlvl_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab_std ~ t_lvl + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
stab_tlvl_ci <- confint(stab_tlvl_boot)

stab_tlvl_sum <- piecewiseSEM::rsquared(stab_tlvl_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_tlvl_pred <- pred_stab_tlvl_mod %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

# get coeff
coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
```
